### 2024-07-14 evaluating-prediction-accuracy.qmd
20240713 - edits

So, to get the chance expectancies of true positives, we would multiply the respective [marginal probabilities](#baseRate), as in Equation @eq-truePositivesByChanceExample:

@@

To get the chance expectancies of true negatives, we would multiply the respective [marginal probabilities](#sec-baseRate), as in @trueNegativesByChanceExample:

@@

```{r}
#| code-fold: true

sampleSize <- 1000

@@

density_data$type <- factor(
  density_data$type,
  levels = c(
    "edible_TN",
    "inedible_TP",
    "edible_FP",
    "inedible_FN"))
```

#No Cutoff
ggplot(
  data = edibleData,
  aes(
    x = score,
    ymin = 0,
    fill = type)) +
  geom_density(alpha = .5) +
  scale_fill_manual(
    name = "Berry Type",
    values = c(
      viridis::viridis(2)[1],
      viridis::viridis(2)[2])) +
  scale_y_continuous(name = "Frequency") +
  theme_bw() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank())
```

@@

```{r}
#| fig-cap: "Receiver Operating Characteristic (ROC) Curves for Various Levels of Area Under The ROC Curve (AUC) for Various Measures."
#| label: fig-aucRange
#| code-fold: true

@@

```{r}
#| label: fig-miscalibration
#| fig-cap: "Types of Miscalibration. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."
#| code-fold: true

>>>>

So, to get the chance expectancies of true positives, we would multiply the respective [marginal probabilities](#baseRate), as in @eq-truePositivesByChanceExample:

@@

To get the chance expectancies of true negatives, we would multiply the respective [marginal probabilities](#sec-baseRate), as in @eq-trueNegativesByChanceExample:

@@

#No Cutoff
sampleSize <- 1000

@@

ggplot(
  data = edibleData,
  aes(
    x = score,
    ymin = 0,
    fill = type)) +
  geom_density(alpha = .5) +
  scale_fill_manual(
    name = "Berry Type",
    values = c(
      viridis::viridis(2)[1],
      viridis::viridis(2)[2])) +
  scale_y_continuous(name = "Frequency") +
  theme_bw() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank())
```

@@

```{r}
#| fig-cap: "Receiver Operating Characteristic (ROC) Curves for Various Levels of Area Under The ROC Curve (AUC) for Various Measures."
#| label: fig-aucRange
#| fig-width: 8
#| fig-height: 8
#| code-fold: true

@@

```{r}
#| label: fig-miscalibration
#| fig-cap: "Types of Miscalibration. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."
#| fig-width: 8
#| fig-height: 8
#| code-fold: true
